---
title: "Thunderstrom Analysis"
output: html_notebook
---
**Imports**
```{r}
library(evd); 
library(evdbayes);
library(coda);
library(ismev);
library(xts);

```


**Loading the Data**

```{r}
load("../data/CAPE_Minder_Rychener_Malsot.RData")
load("../data/NINO34.RData")
load("../data/SRH_Minder_Rychener_Malsot.RData")
```

**Generate PROD**
```{r}
prod = sqrt(cape)*srh
```




** Create Time Series Objects **
```{r}
dates <- seq.Date(as.Date("1979-1-1"), as.Date("2015-12-31"), by=1)
feb29ix <- format(as.Date(dates), "%m-%d") == "02-29"
dates <- dates[!feb29ix]

prod_ts = xts(prod, order.by = rep(dates, each=8))
```



**Beginning the Analysis**
```{r}
get_monthly = function(x) {
  output = list()
  len = nrow(x)
  
  # Get month of element
  month = time(x)
  month = gsub("....-", "", month)
  month = gsub("-..", "", month)
  month = gsub("0","", month)
  for (i in 1:12) {
    output[[i]] = x[month == i,]
  }
  names(output) = c("jan","feb","mar","apr","may","jun","jul","aug","sep","oct","nov","dec")
  return(output)
}

monthly_max = get_monthly(apply.monthly(prod_ts, max))
r = 2
r_monthly_max = get_monthly(apply.monthly(prod_ts, function(x) order(x, decreasing=T)[1:r]))
```


```{r}
# get the monthly maxima of prod
m1 = as.data.frame(apply.monthly(prod_ts, max))$V1;
# produce the gumbel qq plot
qqplot(qgumbel(c(1:length(m1))/(length(m1)+1)),m1,main = "Gumbell Q-Q Plot",xlab = "Theoretical Quantiles", ylab = "Sample Quantiles") ;
```
The qq plot doesn't fit very well, especially in the lower tail. This is likely due
to seasonal dependence.

**Fitting GEV to the entire data**
```{r}
# fit gevd with MLE and produce diagnostic plots
fitmax.MLE<-fgev(m1,method="Nelder-Mead")
par(mfrow=c(2,2))
fitmax.MLE
plot(fitmax.MLE)
```
Poor fit, probably because the distribution isn't stationary. This is especially 
visible in the Probability plot, in which the confidence band is surpassed, 
indicating a poor fit.


```{r}
# fit gevd with Bayesian Techniques
# use the previous outputs (rounded) as initial values (use a different shape)
init<-c(1.6e4,4e3,0.1)
# arbitrary priors
mat <- diag(c(10000,10000,100)) 
pn <- prior.norm(mean=c(0,0,0),cov=mat)
# proposal standard deviation (found by trial and error to get 20%<acceptance rate<40%)
psd<-c(500,0.03,0.02)
# draw 3k samples from markov chain
nit = 30000
thinning = 300
post<-posterior(nit, init=init,prior=pn,lh="gev",data=m1,psd=psd)
# diagnostic plots
MCMC<-mcmc(post[1:nit %% thinning == 0, ], thin=300) 
plot(MCMC) 
attr(mcmc(post),"ar")

```


```{r}
#MCMC_stab <- mcmc(post, thin=50, start=1000)
acf(mcmc(post[1:nit %% thinning == 0, ]))
```
We observe that there seem to be no substantial issues from the autocorrelation 
plots. 

```{r}
apply(mcmc(post[1:nit %% thinning == 0, ]),2,mean)
apply(mcmc(post[1:nit %% thinning == 0, ]),2,sd)

```

** Fit per month only **
```{r}
monthly_fits = lapply(monthly_max, fgev, method="Nelder-Mead", std.err=FALSE)
```




```{r}
# fit the r largest method
#rl = rlarg.fit(data)
data(venice)
venfit <- rlarg.fit(venice[,-1])
```


**PART 2**
```{r}
#plot the maximum as a function of ENSO
plot(nino34,m1,main = "Comparison of Monthly Maxima of PROD vs ENSO",xlab = "ENSO", ylab = "Monthly Maxima of PROD")
n_years = length(m1)/12
month_indexes = rep(c(1,2,3,4,5,6,7,8,9,10,11,12),n_years)
plot(month_indexes,m1,main = "Monthly Maxima of PROD",xlab = "Month", ylab = "Monthly Maxima of PROD")
```
```{r}
# plot the chi plot for dependance analysis
dat.m1_month = cbind(m1,month_indexes);
dat.m1_nino = cbind(m1,nino34);
chiplot(dat.m1_month);
chiplot(dat.m1_nino);
```



**PART 3**
We will now analyse temporal clustering of extremes. For this, we will use the exiplot function from the evd library.

```{r}
# get sample quantiles (used as plotting thresholds)
prod.quantiles = quantile(prod, c(0.8, 0.85, 0.9, 0.95,0.99,0.999))
exiplot(prod,prod.quantiles,main = "Analyiss of Extremal clustering",xlab = "Threshold", ylab = "Extremal Index")
```

We observe that the extremal index is ~0.2, we can therefore conclude that we have strong dependance of extremes, with the limiting mean cluster size being roughly 5. The clustering has no effect for estimaters based on the (monthly) maximum, but the r largest estimator is influenced by it.
